\textbf{EECS 340: Assignment 3}

### 2020-02-21 assignment_3/article.tex
🔨 Update Q1(c) w/ proof on af(n/b)<=cf(n) to concur with case 3 prereq.

We may rewrite it as $T(n) = T\Big(\frac{n}{\frac{1}{\lambda}}\Big) + n^{\lambda}$. Thus, we have a comparsion between $n^{\log_{\frac{1}{\lambda}} 1}$ and $n^{\lambda}$, which is equivalent as $n^0$ and $n^{\lambda}$, then we have $f(n) = \Omega(n^{\log_b a + \epsilon})$ for $\epsilon = \lambda$. We may also show $af(\frac{n}{b}) \leq cf(n)$ for $1 \cdot f\Big(\frac{n}{\frac{1}{\lambda}}\Big) = f(\lambda n)$. Combined, together, we can apply \textit{case 3} of the master theorem and conclude that the solution is $T(n) = \Theta(n^\lambda)$.

>>>>

We may rewrite it as $T(n) = T\Big(\frac{n}{\frac{1}{\lambda}}\Big) + n^{\lambda}$. Thus, we have a comparsion between $n^{\log_{\frac{1}{\lambda}} 1}$ and $n^{\lambda}$, which is equivalent as $n^0$ and $n^{\lambda}$, then we have $f(n) = \Omega(n^{\log_b a + \epsilon}) = \Omega(n^{0 + \epsilon})$ for $\epsilon = \lambda$.

We may also show $af(\frac{n}{b}) \leq cf(n)$ for $c = \lambda^\lambda$; as $af(\frac{n}{b})  = 1 \cdot f\Big(\frac{n}{\frac{1}{\lambda}}\Big) = f(\lambda n) = (\lambda n)^{\lambda}$, where $(\lambda n)^{\lambda} \leq cf(n) =  \lambda^\lambda \cdot n^{\lambda}$. Combined the above two proofs together, we can apply \textit{case 3} of the master theorem and conclude that the solution is $T(n) = \Theta(n^\lambda)$.
